Daily goals

### 2020-07-01 _TODO.Rmd
cleaning todos

- [ ] Do not cite Felsenstein 1985 for bootstrap, just the call that we use for RAxML:
rax_ex, "-T", "{}".format(self.config.num_threads),
                                 "-m", "GTRCAT",
                                 "-s", alignment,
                                 "-p", "1", "-b", "1", "-#", str(num_reps),
                                 "-n", "BOOT{}".format(self.date)
- [ ] Finding a tree to update
  - [ ]  Using the curator website. Mention that there is a differnce between focal clade and ingroup. Physcraper does not take into account the focal clade from Open Tree. Because that is arbitrarily assigned by a curator. The focal clade is a search MRCA more than a taxonomic MRCA, physcraper's default is to get the ingroup from Otol, which is not the focal group.
  - [ ] The link between the ingroup and the search taxon.

@@

- [ ] bootsrap: is it classic [@felsenstein1985confidence] or transfer bootstrap expectation [@lemoine2018renewing]

@@

>>>>

- [ ] Finding a tree to update
  - [ ]  Using the curator website. Mention that there is a differnce between focal clade and ingroup. Physcraper does not take into account the focal clade from Open Tree. Because that is arbitrarily assigned by a curator. The focal clade is a search MRCA more than a taxonomic MRCA, physcraper's default is to get the ingroup from Otol, which is not the focal group.
  - [ ] The link between the ingroup and the search taxon.

@@

@@

- [x] Do not cite Felsenstein 1985 for bootstrap, just explain it while explaining each argument from the call that we use for RAxML:
  rax_ex, "-T", "{}".format(self.config.num_threads),
                                   "-m", "GTRCAT",
                                   "-s", alignment,
                                   "-p", "1", "-b", "1", "-#", str(num_reps),
                                   "-n", "BOOT{}".format(self.date)

- [x] bootsrap: is it classic [@felsenstein1985confidence] or transfer bootstrap expectation [@lemoine2018renewing]
  - probably classic, but we are not citing, just explaining, see point above.
